Community-Conditioned Language Models

### 2021-05-28 paper/paper.tex
with 10 random samples

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have experimentally computed \(d(L,S)\) for five random  ``embeddings'' 
with the same shape as the CCLM embeddings.
We observed a mean of \(μ_d=431.39\) and a (Bessel's-corrected) 
standard deviation \(s_d=3.94\) in their distance from the social embedding, \(S\). %\jp{Unfortunate overloading} luckily it seems that sample stdev is often written with an $s$ to differentiate from population stdev

Thus if \(d(L,S)\) is below \(419.56\)
($\mu_d - 3s_d$), 
we can safely assume that there 
is statistically significant correlation between \(L\) and
\(S\). 
Indeed, this is very clearly the case (\cref{tab:embedding-correlations}),
meaning that the CCLM embedding capture some of the same information as the
social-network embeddings.
We also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\). To
do so we plot the projection of embeddings on along \(U_0\) and
\(U_1\), together with the corresponding singular values.

\begin{table}
\centering
\begin{tabular}{llcc}
\toprule
                        &   & LSTM     & Transformer \\
\midrule
  \multirow{4}{*}{$l_c$}  & 0 &         254.06  (44.99) &         239.41  (49.09)  \\
                          & 1 &         245.14  (47.25) & \textbf{232.18} (50.38)   \\
                          & 2 &         249.17  (46.23) &         233.47  (50.21)  \\
                          & 3 & \textbf{241.13} (48.27) &         237.74   (49.13) \\
\bottomrule
\end{tabular}
\caption{Distance between CCLM embeddings and the social network-based embedding
of \citet{Kumar2018}, as measured by $d(L,S)$. In parentheses is the number of standard deviations
from the mean distance of our random embedding sample.} \label{tab:embedding-correlations}
\end{table}

>>>>

To get a more precise sense of what value of \(d(L,S)\) indicates significant correlation,
We have experimentally computed \(d(L,S)\) for five random  ``embeddings'' 
with the same shape as the CCLM embeddings.
We observed a mean of \(μ_d=431.39\) and a (Bessel's-corrected) 
standard deviation \(s_d=2.90\) in their distance from the social embedding, \(S\). %\jp{Unfortunate overloading} luckily it seems that sample stdev is often written with an $s$ to differentiate from population stdev

Thus if \(d(L,S)\) is below \(422.79\)
($\mu_d - 3s_d$), 
we can safely assume that there 
is statistically significant correlation between \(L\) and
\(S\). 
Indeed, this is very clearly the case (\cref{tab:embedding-correlations}),
meaning that the CCLM embedding capture some of the same information as the
social-network embeddings.
We also give a sense of \emph{how} the
correlation is manifested by analysis of the two principal components
of correlation in the linguistic embeddings, \(U_0\) and \(U_1\). To
do so we plot the projection of embeddings on along \(U_0\) and
\(U_1\), together with the corresponding singular values.

\begin{table}
\centering
\begin{tabular}{llcc}
\toprule
                        &   & LSTM     & Transformer \\
\midrule
  \multirow{4}{*}{$l_c$}  & 0 &         254.06  (61.21) &         239.41  (66.79)  \\
                          & 1 &         245.14  (64.29) & \textbf{232.18} (68.54)   \\
                          & 2 &         249.17  (62.90) &         233.47  (68.32)  \\
                          & 3 & \textbf{241.13} (65.67) &         237.74   (66.84) \\
\bottomrule
\end{tabular}
\caption{Distance between CCLM embeddings and the social network-based embedding
of \citet{Kumar2018}, as measured by $d(L,S)$. In parentheses is the number of standard deviations
from the mean distance of our random embedding samples.} \label{tab:embedding-correlations}
\end{table}
